% ------------------------------------------------------------------
% HEADER (\CONTACTLINE must be defined by the driver file before \input-ing this)
% ------------------------------------------------------------------
\begin{center}
  {\Huge\bfseries \NAME}\\[2pt]
  {\small Daniel Eduardo Pedroza Rodr\'iguez, 24}\\[3pt]
  {\color{accentline}\bfseries \ROLE}\\[4pt]
  {\small \CONTACTLINE}
\end{center}
\vspace{2pt}
\textcolor{accentline}{\rule{\linewidth}{1.2pt}}
\vspace{10pt}

% ------------------------------------------------------------------
\section*{PROFILE}
Computer Systems Engineer graduated from the Universidad Politécnica de Aguascalientes. I've built custom software ranging from web and mobile applications to backend APIs and industrial IoT monitoring systems, working comfortably with both relational and non-relational databases and containerized deployments. I especially enjoy building internal tools that give teams better visibility into their work and help prevent problems before they happen.

% ------------------------------------------------------------------
\section*{EXPERIENCE}

\entry{Developer}{Hecort Manufactura}{1 year 7 months}{
Developed an internal project tracking tool that let the team manage tasks, log issues, and monitor time spent on each project. Also built an IoT monitoring system for industrial machines, using smart sensors with Bluetooth connectivity to detect anomalies in real time, helping the team log incidents early and prevent equipment failures.
}

\entry{Developer}{MegaPCs}{6 months}{
Developed a multiplatform system for managing computer equipment, with features for adding images, printing receipts, and supporting multiple employees.
}

\entry{Assistant}{Jachi}{1 year}{
Performed hardware and software maintenance, installed operating systems and Office, and cleaned printers.
}

% ------------------------------------------------------------------
\section*{EDUCATION}

\entry{Bachelor's Degree in Computer Systems Engineering}{Universidad Politécnica de Aguascalientes}{}{
A program covering the full software development lifecycle: structured and object-oriented programming, web and mobile applications, databases, computer networks, artificial intelligence, data science, and information security, reinforced by an integrative project each term.
}

\entry{Technical Degree in Programming}{CECyTEJ 10}{}{
High school program with a technical specialization in programming, including courses in programming languages, web development, database management, and computer maintenance.
}

% ------------------------------------------------------------------
\section*{TECHNICAL SKILLS}
\begin{tabularx}{\linewidth}{@{}lX@{}}
\textbf{\color{navy}Languages:} & TypeScript, JavaScript, Python, C\#, Dart, Java \\[3pt]
\textbf{\color{navy}Frontend:} & React, Next.js, Tailwind CSS, Flutter \\[3pt]
\textbf{\color{navy}Backend:} & Node.js, Express.js, FastAPI, .NET \\[3pt]
\textbf{\color{navy}Databases:} & PostgreSQL, MongoDB, MySQL, SQL Server, SQLite, Firebase \\[3pt]
\textbf{\color{navy}Infrastructure:} & Docker, RabbitMQ, MQTT, Git \\
\end{tabularx}

% ------------------------------------------------------------------
\section*{FEATURED PROJECTS}
\begin{itemize}[leftmargin=14pt, itemsep=4pt, topsep=2pt]
  \item \textbf{Bluesensor} --- Industrial IoT platform for real-time vibration and temperature monitoring of manufacturing equipment, with configurable alerts. React, TypeScript, FastAPI, PostgreSQL, Docker.
  \item \textbf{LogHub} --- Centralized logging service for consolidating and querying logs across multiple applications. React, FastAPI, RabbitMQ, PostgreSQL, Docker.
  \item \textbf{Inventory Management System} --- Inventory system with Active Directory authentication. Flutter, .NET, SQL Server.
\end{itemize}
